Patterns in Knowledge Production: Political Ruptures and Imperial Dynamics Shaping Public Discourse in Sweden and Finland, 1640–1828

### 2017-11-17 inst/examples/20170201-manuscript.Rmd
ok

---
title: "Patterns in Knowledge Production: Political Ruptures and Imperial Dynamics Shaping Public Discourse in Sweden and Finland, 1640–1828"
author: "Mikko Tolonen, Leo Lahti, Hege Roivainen, Jani Marjanen"
date: "`r Sys.Date()`"
output: 
  beamer_presentation:
    theme: "boxes"
    colortheme: "orchid"
    fonttheme: "professionalfonts"
    dev: "png"
fontsize: 12pt
---

@@

knitr::opts_chunk$set(echo = FALSE)
knitr::opts_chunk$set(fig.path = "20170201_manuscript/", dpi = 300)
#knitr::opts_chunk$set(dev = "cairo_postscript") # Embed fonts
# knitr::opts_chunk$set(dev = c("png", "svg")) # Embed fonts
knitr::opts_chunk$set(out.width = "17cm") # Default size 8.5cm ie 3.35 inch) per col
knitr::opts_chunk$set(out.format = "latex")

@@

```{r Figure_1, message=FALSE, warning=FALSE, fig.width=10, fig.height=4, echo=FALSE}

#message=FALSE, warning=FALSE, fig.width=10, fig.height=4, echo=FALSE, dpi=300, dev="postscript", out.format="latex", out.width="30%"

@@

>>>>

---
title: "Patterns in Knowledge Production: Political Ruptures and Imperial Dynamics Shaping Public Discourse in Sweden and Finland, 1640–1828"
author: "Mikko Tolonen, Leo Lahti, Hege Roivainen, Jani Marjanen"
date: "`r Sys.Date()`"
output: 
  beamer_presentation:
    theme: "boxes"
    colortheme: "orchid"
    fonttheme: "professionalfonts"
    dev: "pdf"
fontsize: 12pt
---

@@

knitr::opts_chunk$set(echo = FALSE)
knitr::opts_chunk$set(fig.path = "20170201_manuscript/", dpi = 300)
knitr::opts_chunk$set(dev = "jpeg", quality = 100) 
#knitr::opts_chunk$set(dev = "cairo_pdf") # Embed fonts
#knitr::opts_chunk$set(dev = "cairo_ps") # Embed fonts
# knitr::opts_chunk$set(dev = c("png")) # Embed fonts
knitr::opts_chunk$set(out.width = "10cm") # Default size 8.5cm ie 3.35 inch) per col
knitr::opts_chunk$set(out.format = "latex")

@@

```{r Figure_1, message=FALSE, warning=FALSE, fig.width=11, fig.height=5, echo=FALSE}

@@

print(p)

#postscript(file = "Figure_1.eps", width = 11, height = 5, paper = "special",
#              family = "sans", bg = "white")
#print(p)
#dev.off()
#library(extrafont)
#embed_fonts("Figure_1.eps", outfile="Figure_1.eps")
```
